R for Clinical Study Reports and Submission

### 2021-11-17 submission-overview.Rmd
update format

> "Sponsors should provide the software programs used to create all ADaM
datasets and **generate tables and figures associated with primary and
secondary efficacy analyses**. Furthermore, sponsors should submit software
programs used to generate additional information included in Section 14
CLINICAL STUDIES of the Prescribing Information (PI)26 if applicable.
**The specific software utilized should be specified in the ADRG**.
The main purpose of requesting the submission of these programs
**is to understand the process by which the variables for the respective
analyses were created and to confirm the analysis algorithms**.
Sponsors should submit software programs in **ASCII text format**;
however, executable file extensions should not be used."

>>>>

::: {.rmdnote}
"Sponsors should provide the software programs used to create all ADaM
datasets and **generate tables and figures associated with primary and
secondary efficacy analyses**. Furthermore, sponsors should submit software
programs used to generate additional information included in Section 14
CLINICAL STUDIES of the Prescribing Information (PI)26 if applicable.
**The specific software utilized should be specified in the ADRG**.
The main purpose of requesting the submission of these programs
**is to understand the process by which the variables for the respective
analyses were created and to confirm the analysis algorithms**.
Sponsors should submit software programs in **ASCII text format**;
however, executable file extensions should not be used."
:::
